Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-18 ms.qmd
Adding some ployt layout features. I think the insets work better

p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])

>>>>

# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork

p <- (zoom_plots[[1]] | zoom_plots[[2]]) /map1_current / (zoom_plots[[3]]) + plot_layout(
  nrow = 3, # 3 rows of plots,
  ncol = 3, # 3 columns of plots,
  heights = c(1, 2, 1), # The first plot is half the size of the second and thrid plot
  widths = c(1, 1, 1) # all plots have equal width
)

map1_current + inset_element(zoom_plots[[1]], left = 0, bottom = 0.95, right = 0.4, top = 1.4, align_to = 'full') + inset_element(zoom_plots[[2]], left = 0.7, bottom =0.95, right = 1, top = 1.4, align_to = 'full') + plot_annotation(tag_levels = "A", tag_suffix = ")")
